\begin{abstract}
AI agents enhanced with tools, particularly code interpreters, hold promising prospects for broad and deep applications. However, existing systems often require reinterpreting problems and generating new codes for similar tasks, rather than reusing previously written and validated functions, leading to inefficiencies in token usage and lack of generalization. In response to these challenges, we introduce \textit{open-creator}, a novel AI agents framework bridging code interpreters and skill libraries. Open-creator is designed to standardize various inputs (including, but not limited to, dialogic problem-solving experiences, code files, and API documentation) into a uniform skill object format. This framework supports local saving, searching, and cloud uploading by users. Adopting a modular strategy, open-creator allows developers and researchers to create, share, and reuse skills without concerns over compatibility or version control. Furthermore, it offers flexibility in modifying, assembling, and disassembling created skills, which is crucial as skills may need updates over time and with changing environments. This mechanism allows AI agents to continually optimize skills based on feedback and new data. Our approach paves the way for more efficient and adaptable AI agent functionalities, contributing to the field's ongoing development. The open-creator code is publicly accessible at: \href{https://github.com/timedomain-tech/open-creator}{https://github.com/timedomain-tech/open-creator}.
\end{abstract}
